Machine Learning Approaches for Ammonia Volatilization Prediction after Manure Application

### 2024-06-26 manuscript.qmd
updating figures, corrections of labels, ...

```{r, fig.height = 12, fig.width = 10}
plot_residuals_complete_dataset = predictions_of_all_methods %>%
    mutate (residuals = truth_er - er) %>%
    mutate (app.mthd = recode (app.mthd, "bc" = "Broadcast", "bsth" = "Trailing hose", "ts" = "Trailing shoe", "os" = "Open slot injection")) %>%
    mutate (app.mthd = factor (app.mthd, levels = c ("Broadcast", "Trailing hose", "Trailing shoe", "Open slot injection"))) %>%
    ggplot () +
        geom_boxplot (aes (x = country, y = residuals, fill = method)) +
        geom_hline (yintercept = 0, linetype = 2) +
        scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
        facet_wrap (~ app.mthd, ncol = 1) +
        ylab ("Residual (frac. applied TAN)") +
        labs (fill = "") +
        theme (legend.position = "bottom",
               axis.title.y = element_text (margin = ggplot2::margin (r = 30)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)))

@@

```{r, fig.height = 12, fig.width = 10}
plot_residuals_evaluation_subset = predictions_of_all_methods %>%
    filter (dataset == "Evaluation subset") %>%
    mutate (residuals = truth_er - er) %>%
    mutate (app.mthd = recode (app.mthd, "bc" = "Broadcast", "bsth" = "Trailing hose", "ts" = "Trailing shoe", "os" = "Open slot injection")) %>%
    mutate (app.mthd = factor (app.mthd, levels = c ("Broadcast", "Trailing hose", "Trailing shoe", "Open slot injection"))) %>%
    ggplot () +
        geom_boxplot (aes (x = country, y = residuals, fill = method), varwidth = TRUE) +
        geom_hline (yintercept = 0, linetype = 2) +
        scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
        facet_wrap (~ app.mthd, ncol = 1) +
        ylab ("Residual (frac. applied TAN)") +
        labs (fill = "") +
        theme (legend.position = "bottom",
               axis.title.y = element_text (margin = ggplot2::margin (r = 30)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)))

@@

    mutate (group = recode (group,
                            "bc shallow 0" = "incorporation",
                            "bsth none -" = "trailing hose",
                            "os none -" = "open slot",
                            "ts none -" = "trailing shoe")) %>%

@@

        geom_boxplot (aes (x = efficacy, y = group, fill = group)) +
        scale_fill_manual (values = Dark2[c(2 : 5)]) +
        ylab ("") + xlab ("Efficacy") +
        theme (legend.position = "none",
               axis.ticks.y = element_blank(),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0))) +
        facet_wrap (~ method, ncol = 1)

>>>>

```{r, fig.height = 12, fig.width = 10}
plot_residuals_complete_dataset = predictions_of_all_methods %>%
    mutate (residuals = truth_er - er) %>%
    mutate (app.mthd = recode (app.mthd, "bc" = "Broadcast", "bsth" = "Trailing hoses", "ts" = "Trailing shoes", "os" = "Open slot injection")) %>%
    mutate (app.mthd = factor (app.mthd, levels = c ("Broadcast", "Trailing hoses", "Trailing shoes", "Open slot injection"))) %>%
    ggplot () +
        geom_boxplot (aes (x = country, y = residuals, fill = method)) +
        geom_hline (yintercept = 0, linetype = 2) +
        scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
        facet_wrap (~ app.mthd, ncol = 1) +
        ylab ("Residual (frac. applied TAN)") +
        labs (fill = "") +
        theme (legend.position = "bottom",
               axis.title.y = element_text (margin = ggplot2::margin (r = 30)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)))

@@

```{r, fig.height = 12, fig.width = 10}
plot_residuals_evaluation_subset = predictions_of_all_methods %>%
    filter (dataset == "Evaluation subset") %>%
    mutate (residuals = truth_er - er) %>%
    mutate (app.mthd = recode (app.mthd, "bc" = "Broadcast", "bsth" = "Trailing hoses", "ts" = "Trailing shoes", "os" = "Open slot injection")) %>%
    mutate (app.mthd = factor (app.mthd, levels = c ("Broadcast", "Trailing hoses", "Trailing shoes", "Open slot injection"))) %>%
    ggplot () +
        geom_boxplot (aes (x = country, y = residuals, fill = method), varwidth = TRUE) +
        geom_hline (yintercept = 0, linetype = 2) +
        scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
        facet_wrap (~ app.mthd, ncol = 1) +
        ylab ("Residual (frac. applied TAN)") +
        labs (fill = "") +
        theme (legend.position = "bottom",
               axis.title.y = element_text (margin = ggplot2::margin (r = 30)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)))

@@

    mutate (group = recode (group,
                            "bc shallow 0" = "incorporation",
                            "bsth none -" = "trailing hoses",
                            "os none -" = "open slot",
                            "ts none -" = "trailing shoes")) %>%

@@

        geom_boxplot (aes (x = efficacy, y = group, fill = group)) +
        scale_fill_manual (values = Dark2[c(2 : 5)]) +
        scale_y_discrete (limits = c ("open slot", "trailing shoes", "trailing hoses", "incorporation")) +
        ylab ("") + xlab ("Efficacy") +
        theme (legend.position = "none",
               axis.ticks.y = element_blank(),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0))) +
        facet_wrap (~ method, ncol = 1)
